Mapping malaria by sharing spatial information between incidence and prevalence datasets

### 2019-12-02 ms.tex
Tidy up.

\title[Mapping malaria by sharing spatial information]{Mapping malaria by sharing spatial information between incidence and prevalence datasets}
\author[Tim C.D. Lucas {\it et al.}]{Tim C.D. Lucas}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\email{timcdlucas@gmail.com}
\author{Anita K. Nandi\textsuperscript{1}}
\author{Elisabeth G. Chestnutt\textsuperscript{1}}
\author{Katherine A. Twohig\textsuperscript{1}}
\author{Suzanne H. Keddie\textsuperscript{1}}
\author{Emma L. Collins\textsuperscript{1}}
\author{Rosalind E. Howes}
\author{Michele Nguyen\textsuperscript{1}}
\author{Susan F. Rumisha\textsuperscript{1}}
\author{Andre Python\textsuperscript{1}}
\author{Rohan Arambepola\textsuperscript{1}}
\author{Amelia Bertozzi-Villa\textsuperscript{1}}
\author{Penelope Hancock\textsuperscript{1}}
\author{Punam Amratia\textsuperscript{1}}
\author{Katherine E. Battle\textsuperscript{1}}
\author{Ewan Cameron\textsuperscript{1}}
\author{Peter W. Gething\textsuperscript{1, 2, 3}}
\author{Daniel J. Weiss\textsuperscript{1}}
\address{1. Big Data Institute,
University of Oxford,
Oxford,
UK.}
\address{2. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia}
\address{3. Curtin University, Perth, Australia}

@@

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Reported incidence data and modelled incidence maps for Senegal. 
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}

@@

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
\caption{\label{predobsmapidn}
Reported incidence data and modelled incidence maps for Indonesia. 
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}
\end{figure}

@@

$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.
The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
This effect modelled extra-binomial sampling noise.
As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.

>>>>

\title[Mapping malaria by sharing spatial information]{Mapping malaria by sharing spatial information between incidence and prevalence datasets}
\author[Tim C.D. Lucas {\it et al.}]{Tim C.D. Lucas}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\email{timcdlucas@gmail.com}
\author{Anita K. Nandi\textsuperscript{1}}
\author{Elisabeth G. Chestnutt\textsuperscript{1}}
\author{Katherine A. Twohig\textsuperscript{1}}
\author{Suzanne H. Keddie\textsuperscript{1}}
\author{Emma L. Collins\textsuperscript{1}}
\author{Rosalind E. Howes\textsuperscript{1}}
\author{Michele Nguyen\textsuperscript{1}}
\author{Susan F. Rumisha\textsuperscript{1}}
\author{Andre Python\textsuperscript{1}}
\author{Rohan Arambepola\textsuperscript{1}}
\author{Amelia Bertozzi-Villa\textsuperscript{1}}
\author{Penelope Hancock\textsuperscript{1}}
\author{Punam Amratia\textsuperscript{1}}
\author{Katherine E. Battle\textsuperscript{1}}
\author{Ewan Cameron\textsuperscript{1}}
\author{Peter W. Gething\textsuperscript{1, 2, 3}}
\author{Daniel J. Weiss\textsuperscript{1}}
\address{1. Big Data Institute,
University of Oxford,
Oxford,
UK.}
\address{2. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia}
\address{3. Curtin University, Perth, Australia}

@@

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Reported incidence data and modelled incidence maps for Senegal. 
The national boundary of Senegal is shown in grey and missing data is left white.
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}

@@

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
\caption{\label{predobsmapidn}
Reported incidence data and modelled incidence maps for Indonesia. 
The national boundary of Indonesia is shown in grey and missing data is left white.
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}
\end{figure}

@@

$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.
The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
This effect modelled extra-binomial sampling noise.
As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.

### 2019-12-02 si.tex
Do KT edits and dont use xr cos it aint working.
Tidy up.

@@

% latex table generated in R 3.4.4 by xtable 1.8-4 package
% Fri Jul 19 12:48:02 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
  \hline
$\beta_0$ & -5.58 & 0.29 & -4.66 & 0.58 & -5.35 & 0.52 \\ 
  $\beta_p$ &  &  &  &  & 1.63 & 0.13 \\ 
  LST day mean & 0.00 & 0.26 & -0.02 & 0.26 & -0.04 & 0.24 \\ 
  EVI & 0.43 & 0.23 & 0.35 & 0.24 & 0.35 & 0.20 \\ 
  TSI & -0.61 & 0.24 & -0.51 & 0.24 & 0.42 & 0.17 \\ 
  accessability & -0.09 & 0.21 & -0.07 & 0.21 & 0.11 & 0.11 \\ 
  elevation & 0.44 & 0.21 & 0.36 & 0.22 & 0.31 & 0.18 \\ 
  LST day SD & 0.23 & 0.20 & 0.07 & 0.21 & 0.24 & 0.20 \\ 
  Night lights & 0.10 & 0.06 & 0.08 & 0.06 & 0.07 & 0.04 \\ 
  TCW & -0.02 & 0.28 & -0.05 & 0.28 & 0.17 & 0.23 \\ 
  Prev GP &  &  & 0.30 & 0.17 &  &  \\ 
  $\omega_v$ & 0.25 & 0.25 & 0.27 & 0.25 & -0.03 & 0.32 \\ 
  $\omega_w$ &  &  &  &  & -1.03 & 0.13 \\ 
  $\log(\sigma_u)$ & -2.48 & 0.61 & -2.53 & 0.63 & -3.35 & 0.52 \\ 
  $\log(\rho)$ & 0.58 & 0.30 & 0.58 & 0.30 & 0.71 & 0.31 \\ 
  $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
   \hline
\end{tabular}
\caption{Parameter estimates for Senegal. $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
\end{table}

% latex table generated in R 3.4.4 by xtable 1.8-4 package
% Fri Jul 19 12:48:37 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
  \hline
$\beta_0$ & -3.81 & 0.32 & -2.66 & 0.29 & -3.77 & 0.30 \\ 
  $\beta_p$ &  &  &  &  & 0.07 & 0.10 \\ 
  LST day mean & 0.16 & 0.29 & 0.14 & 0.27 & 0.14 & 0.24 \\ 
  EVI & 0.34 & 0.21 & 0.23 & 0.19 & 0.46 & 0.13 \\ 
  TSI & 0.45 & 0.22 & 0.42 & 0.21 & 0.63 & 0.19 \\ 
  accessability & 0.36 & 0.11 & 0.15 & 0.10 & 0.24 & 0.07 \\ 
  elevation & -0.11 & 0.18 & -0.05 & 0.16 & 0.31 & 0.12 \\ 
  LST day SD & -0.22 & 0.21 & -0.15 & 0.17 & -0.20 & 0.15 \\ 
  Night lights & -0.01 & 0.03 & -0.02 & 0.02 & -0.02 & 0.02 \\ 
  TCW & -0.26 & 0.26 & -0.22 & 0.25 & -0.15 & 0.15 \\ 
  Prev GP &  &  & 0.36 & 0.07 &  &  \\ 
  $\omega_v$ & 1.19 & 0.23 & 1.26 & 0.23 & 1.38 & 0.26 \\ 
  $\omega_w$ &  &  &  &  & -0.77 & 0.11 \\ 
  $\log(\sigma_u)$ & -2.57 & 0.60 & -2.83 & 0.63 & -3.21 & 0.49 \\ 
  $\log(\rho)$ & 0.99 & 0.32 & 0.69 & 0.31 & 0.73 & 0.27 \\ 
  $\log(\alpha)$ &  &  &  &  & 0.00 & 0.00 \\ 
   \hline
\end{tabular}
\caption{Parameter estimates for Madagascar $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
\end{table}

% latex table generated in R 3.4.4 by xtable 1.8-4 package
% Fri Jul 19 12:48:41 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
  \hline
$\beta_0$ & -5.83 & 0.65 & -5.59 & 0.80 & -6.31 & 0.56 \\ 
  $\beta_p$ &  &  &  &  & 0.03 & 0.20 \\ 
  LST day mean & -0.03 & 0.20 & -0.03 & 0.20 & 0.28 & 0.27 \\ 
  EVI & 0.11 & 0.08 & 0.11 & 0.08 & 0.55 & 0.18 \\ 
  TSI & 0.24 & 0.19 & 0.24 & 0.19 & -0.02 & 0.24 \\ 
  accessability & 0.73 & 0.24 & 0.73 & 0.24 & 0.36 & 0.19 \\ 
  elevation & -0.12 & 0.12 & -0.12 & 0.12 & -0.23 & 0.22 \\ 
  LST day SD & 0.04 & 0.11 & 0.04 & 0.11 & -0.04 & 0.18 \\ 
  Night lights & -0.34 & 0.12 & -0.34 & 0.12 & 0.01 & 0.10 \\ 
  TCW & 0.05 & 0.10 & 0.05 & 0.10 & 0.06 & 0.19 \\ 
  Prev GP &  &  & 0.06 & 0.12 &  &  \\ 
  $\omega_v$ & -1.54 & 0.11 & -1.54 & 0.11 & -1.33 & 0.11 \\ 
  $\omega_w$ &  &  &  &  & -2.65 & 0.09 \\ 
  $\log(\sigma_u)$ & -2.23 & 0.43 & -2.25 & 0.43 & -2.79 & 0.48 \\ 
  $\log(\rho)$ & 1.63 & 0.23 & 1.62 & 0.23 & 1.38 & 0.24 \\ 
  $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
   \hline
\end{tabular}
\caption{Parameter estimates for Indonesia $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
\end{table}

@@

\clearpage
\subsection{Full model fields}

\subsubsection{Senegal}
\begin{figure}[h!]
\centering

\includegraphics[width = 0.3\textheight]{figures/sen_prevgp.png}

\caption{The prevalence GP model that is used as a covariate.}
\label{gpsencov}
\end{figure}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldsen}
\end{figure}
\begin{figure}[h!]
\centering

\includegraphics[width = 0.3\textheight]{figures/sen_prgp_field.png}

\caption{The random field as fitted to all the data in the prevalence GP model.}
\label{gpfieldsen}
\end{figure}

@@

\clearpage
\subsubsection{Indonesia}
\begin{figure}[h!]
\centering

\includegraphics[width = 0.6\textheight]{figures/idn_prevgp.png}

\caption{The prevalence GP model that is used as a covariate.}
\label{gpidncov}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\label{baselinefieldidn}
\end{figure}

\includegraphics[width =  0.6\textheight]{figures/idn_prgp_field.png}

\caption{The random field as fitted to all the data in the joint model.}
\label{gpfieldidn}
\end{figure}

@@

\clearpage
\subsubsection{Madagascar}
\begin{figure}[h!]
\centering

\includegraphics[width =  0.3\textheight]{figures/mdg_prevgp.png}

\caption{The prevalence GP model that is used as a covariate.}
\label{gpmdgcov}
\end{figure}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldmdg}
\end{figure}
\begin{figure}[h!]
\centering

\includegraphics[width = 0.3\textheight]{figures/mdg_prgp_field.png}

\caption{The random field as fitted to all the data in the prevalence GP model.}
\label{gpfieldmdg}
\end{figure}

>>>>

\usepackage{subfig}

@@

% latex table generated in R 3.4.4 by xtable 1.8-4 package
% Fri Jul 19 12:48:02 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
  \hline
$\beta_0$ & -5.58 & 0.29 & -4.66 & 0.58 & -5.35 & 0.52 \\ 
  $\beta_p$ &  &  &  &  & 1.63 & 0.13 \\ 
  LST day mean & 0.00 & 0.26 & -0.02 & 0.26 & -0.04 & 0.24 \\ 
  EVI & 0.43 & 0.23 & 0.35 & 0.24 & 0.35 & 0.20 \\ 
  TSI & -0.61 & 0.24 & -0.51 & 0.24 & 0.42 & 0.17 \\ 
  accessability & -0.09 & 0.21 & -0.07 & 0.21 & 0.11 & 0.11 \\ 
  elevation & 0.44 & 0.21 & 0.36 & 0.22 & 0.31 & 0.18 \\ 
  LST day SD & 0.23 & 0.20 & 0.07 & 0.21 & 0.24 & 0.20 \\ 
  Night lights & 0.10 & 0.06 & 0.08 & 0.06 & 0.07 & 0.04 \\ 
  TCW & -0.02 & 0.28 & -0.05 & 0.28 & 0.17 & 0.23 \\ 
  Prev GP &  &  & 0.30 & 0.17 &  &  \\ 
  $\omega_v$ & 0.25 & 0.25 & 0.27 & 0.25 & -0.03 & 0.32 \\ 
  $\omega_w$ &  &  &  &  & -1.03 & 0.13 \\ 
  $\log(\sigma_u)$ & -2.48 & 0.61 & -2.53 & 0.63 & -3.35 & 0.52 \\ 
  $\log(\rho)$ & 0.58 & 0.30 & 0.58 & 0.30 & 0.71 & 0.31 \\ 
  $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
   \hline
\end{tabular}
\label{parssen}
\caption[Parameter estimates for Senegal]{Parameter estimates for Senegal. $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
\end{table}

% latex table generated in R 3.4.4 by xtable 1.8-4 package
% Fri Jul 19 12:48:37 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
  \hline
$\beta_0$ & -3.81 & 0.32 & -2.66 & 0.29 & -3.77 & 0.30 \\ 
  $\beta_p$ &  &  &  &  & 0.07 & 0.10 \\ 
  LST day mean & 0.16 & 0.29 & 0.14 & 0.27 & 0.14 & 0.24 \\ 
  EVI & 0.34 & 0.21 & 0.23 & 0.19 & 0.46 & 0.13 \\ 
  TSI & 0.45 & 0.22 & 0.42 & 0.21 & 0.63 & 0.19 \\ 
  accessability & 0.36 & 0.11 & 0.15 & 0.10 & 0.24 & 0.07 \\ 
  elevation & -0.11 & 0.18 & -0.05 & 0.16 & 0.31 & 0.12 \\ 
  LST day SD & -0.22 & 0.21 & -0.15 & 0.17 & -0.20 & 0.15 \\ 
  Night lights & -0.01 & 0.03 & -0.02 & 0.02 & -0.02 & 0.02 \\ 
  TCW & -0.26 & 0.26 & -0.22 & 0.25 & -0.15 & 0.15 \\ 
  Prev GP &  &  & 0.36 & 0.07 &  &  \\ 
  $\omega_v$ & 1.19 & 0.23 & 1.26 & 0.23 & 1.38 & 0.26 \\ 
  $\omega_w$ &  &  &  &  & -0.77 & 0.11 \\ 
  $\log(\sigma_u)$ & -2.57 & 0.60 & -2.83 & 0.63 & -3.21 & 0.49 \\ 
  $\log(\rho)$ & 0.99 & 0.32 & 0.69 & 0.31 & 0.73 & 0.27 \\ 
  $\log(\alpha)$ &  &  &  &  & 0.00 & 0.00 \\ 
   \hline
\end{tabular}
\label{parsmdg}
\caption{Parameter estimates for Madagascar $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
\end{table}

% latex table generated in R 3.4.4 by xtable 1.8-4 package
% Fri Jul 19 12:48:41 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
  \hline
$\beta_0$ & -5.83 & 0.65 & -5.59 & 0.80 & -6.31 & 0.56 \\ 
  $\beta_p$ &  &  &  &  & 0.03 & 0.20 \\ 
  LST day mean & -0.03 & 0.20 & -0.03 & 0.20 & 0.28 & 0.27 \\ 
  EVI & 0.11 & 0.08 & 0.11 & 0.08 & 0.55 & 0.18 \\ 
  TSI & 0.24 & 0.19 & 0.24 & 0.19 & -0.02 & 0.24 \\ 
  accessability & 0.73 & 0.24 & 0.73 & 0.24 & 0.36 & 0.19 \\ 
  elevation & -0.12 & 0.12 & -0.12 & 0.12 & -0.23 & 0.22 \\ 
  LST day SD & 0.04 & 0.11 & 0.04 & 0.11 & -0.04 & 0.18 \\ 
  Night lights & -0.34 & 0.12 & -0.34 & 0.12 & 0.01 & 0.10 \\ 
  TCW & 0.05 & 0.10 & 0.05 & 0.10 & 0.06 & 0.19 \\ 
  Prev GP &  &  & 0.06 & 0.12 &  &  \\ 
  $\omega_v$ & -1.54 & 0.11 & -1.54 & 0.11 & -1.33 & 0.11 \\ 
  $\omega_w$ &  &  &  &  & -2.65 & 0.09 \\ 
  $\log(\sigma_u)$ & -2.23 & 0.43 & -2.25 & 0.43 & -2.79 & 0.48 \\ 
  $\log(\rho)$ & 1.63 & 0.23 & 1.62 & 0.23 & 1.38 & 0.24 \\ 
  $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
   \hline
\end{tabular}
\label{parsidn}
\caption{Parameter estimates for Indonesia $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
\end{table}

@@

\clearpage

\subsection{Full model fields}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldsen}
\end{figure}

\begin{figure}[h!]
     \centering
     \subfloat[][The prevalence GP model that is used as a covariate.]{\includegraphics[width = 0.3\textheight]{figures/sen_prevgp.png}}
     \subfloat[][The random field as fitted to all the data in the prevalence GP model.]{\includegraphics[width = 0.3\textheight]{figures/sen_prgp_field.png}}
     \label{gpsencov}
\end{figure}
%remaining part

@@

\clearpage
\subsubsection{Indonesia}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldidn}
\end{figure}

\begin{figure}[h!]
     \centering
     \subfloat[][The prevalence GP model that is used as a covariate.]{\includegraphics[width =0.5\textwidth ]{figures/idn_prevgp.png}}
     \subfloat[][The random field as fitted to all the data in the prevalence GP model.]{\includegraphics[width = 0.5\textwidth]{figures/idn_prgp_field.png}}
     \label{gpsencov}
\end{figure}
%remaining part

@@

\clearpage
\subsubsection{Madagascar}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldmdg}
\end{figure}

\begin{figure}[h!]
     \centering
     \subfloat[][The prevalence GP model that is used as a covariate.]{\includegraphics[width =0.5\textwidth ]{figures/mdg_prevgp.png}}
     \subfloat[][The random field as fitted to all the data in the prevalence GP model.]{\includegraphics[width = 0.5\textwidth]{figures/mdg_prgp_field.png}}
     \label{gpsencov}
\end{figure}
%remaining part
